---
output:
  html_document: default
  pdf_document:
    fig_crop: no
    keep_tex: yes
---

```{r echo=FALSE}
library(knitr)
opts_chunk$set(cache=F, autodep=TRUE, out.width = "\\textwidth", fig.height = 6, fig.width = 8,  dpi = 300, warning=F, message=F, dev = "png")
options(width = 86)
```

In the following appendix, I present the `R Code` to reproduce the 
truth tables and analyses in Chapter 5. I do not print the truth tables, here, 
as they are already included in the chapter. In addition, I add some 
illustrations and graphs for the QCA analyses. Also, I show the results of some
individual analyses that I do not present in chapter 5. They are for illustration
purposes.

First, I load the required R packages[^1]:
```{r setup, message=FALSE}
library(QCA)
library(QCA3)
library(wordcloud)
library(SetMethods)
library(car)
library(VennDiagram)
```

[^1]: Dusa, Adrian and Alrik Thiem (2014). QCA: A Package for Qualitative Comparative Analysis. R package version 1.1-3. URL: http://cran.r-project.org/package=QCA.
Fellows, Ian (2014). wordcloud: Word Clouds. R package version 2.5. URL: http://CRAN.R-project.org/package=wordcloud.
Fox, John and Sanford Weisberg (2011). An {R} Companion to Applied Regression,  Second Edition. Thousand Oaks CA: Sage. URL: http://socserv.socsci.mcmaster.ca/jfox/Books/Companion.
Huang, Ronggui. (2014). QCA3: Yet another package for Qualitative Comparative Analysis. R package version 0.0-7. URL: http://asrr.r-forge.r-project.org/.
Quaranta, Mario  (2013). SetMethods: A Package Companion to "Set-Theoretic Methods for the Social Sciences". R package version 1.0. URL: http://CRAN.R-project.org/package=SetMethods.


Next, I import the raw data and create an empty data-set for the QCA data:
```{r import}
data <- read.csv("../data/raw-data.csv")
data$X <- NULL # clean up import artifact
data$cases <-  paste(data$IO, data$Year, sep = "") # name cases
data_qca <- as.data.frame(matrix(0, ncol = 0, nrow = 70))
data_qca$cases <- data$cases
# add case names as row names
row.names(data_qca) <- data_qca$cases
```



#Calibration
The following code-blocks show the steps I took to calibrate the data-set. Again, 
the detailed description is included in Chapter 5.

##Talk
```{r}
thr1 <- 1
data_qca$TALK.Part <- c(thr1, 1, 1, thr1, thr1, rep(0, 31), rep(thr1, 5),
            1,thr1, rep(1, 3), rep(thr1, 3), 1, rep(thr1, 4), 1, 0, 1, 1, 
            rep(thr1, 10), 1, 1)
data_qca$TALK.Trans <- c(rep(0, 36), rep(thr1, 9), 1, rep(thr1, 8), 1, 0, 
            rep(thr1, 2), 1, thr1, thr1, 1, rep(thr1, 7), 1)
```

## Decision
```{r}
thr1 <- 0
thr2 <- 1
data_qca$DEC.Part <- c(rep(0, 15), rep(1, 4), rep(0, 36), rep(1, 7), 
            rep(0,8))

data_qca$DEC.Trans <- c(rep(0, 29), rep(thr1, 7), rep(thr2, 7), 
            rep(1, 12), 0, thr1, rep(thr2, 11), rep(1, 2))
```

## Action
```{r}
data_qca$ACT.Part.1 <-  c(0, rep(1, 7), rep(0, 26), rep(1, 21), rep(1, 4), 
            rep(0, 8), rep(1, 3))
data_qca$ACT.Part.2 <-  c(rep(0, 51), rep(1, 4), rep(0, 12), rep(1, 3))
data_qca$ACT.Part.4 <-  c(rep(0, 25), rep(1, 13), rep(0, 3), rep(1, 5), 
            rep(0, 2), rep(1, 7), rep(0, 7), rep(1, 3),0, 0, 1, 1, 1)
data_qca$ACT.Trans <- c(rep(0, 4), rep(1, 3), rep(0, 38), rep(1, 10),
            rep(0, 7), rep(1, 4), rep(0, 4))
```

## Resource-based conditions
```{r}
thr1 <- 1
data_qca$RB.Budget <-  c(rep(0, 26), rep(thr1, 4), rep(0, 6), rep(thr1, 9), 
            rep(0, 10), rep(0, 2), rep(1, 4), rep(0, 6), rep(thr1, 3))
data_qca$RB.Inequality <-  recode(data$RB.Inequality, 
            recodes = "0:0.8126000=0; 0.8126313:0.9=1")
data_qca$RB.Complexity <- c(rep(1, 55), rep(0, 15))
```

## Norm-based conditions
```{r}
thr1 <- 1
data_qca$NB.visibility.all <-  c(rep(0, 29), rep(thr1, 5), rep(1, 4), 
            rep(thr1, 7), rep(1, 6), rep(thr1, 3), 1, rep(0, 15))
data_qca$NB.visibility.hl <-  c(rep(0, 29), rep(1, 3), rep(0, 10), 
            rep(1, 5), rep(0, 5), rep(1, 3), rep(0, 15))
data_qca$NB.gov.depth <- c(rep(0, 13), rep(0, 21), rep(1, 21), rep(0, 15))
data_qca$NB.dem.mem <-  c(rep(0, 36), rep(1, 19), rep(0, 7), rep(1, 8))
data_qca$NB.og.norm <-  c(rep(0, 33), rep(thr1, 6), rep(1, 16), rep(1, 15))

```

# QCA analyses
Next, I present the analysis of the individual outcome variables and of some
combined outcomes. In the analysis for sufficiency, I limit the presentation
to the intermediate solution for those analyses I do not present in more
detail in Chapter 5.

## Participation Talk
```{r part_talk}
#truth table w/o IAEA1957:1961, OPCW 1997
data_qca$TALKPART <- data_qca$TALK.Part # for QCA package conventions
tt <- truthTable(data_qca[c(6:55, 57:70), c(18, 10:17)], outcome = 
            c("TALKPART"), incl.cut1=1, sort.by="incl", 
            show.cases = TRUE)

# necessary conditions for participation talk
superSubset(data_qca[c(6:55, 57:70), c(18, 10:17)], outcome = 
            "TALKPART", relation="necessity", incl.cut=1, cov.cut=0.8)
# neg. outcome, to check for contradictions
superSubset(data_qca[c(6:55, 57:70), c(18, 10:17)], outcome = 
            "TALKPART", relation="necessity", incl.cut=1, cov.cut=1, 
            neg.out = T)
```

```{r talk_part_nc, echo=FALSE, eval = F}
textplot(x = data_qca$NB.og.norm[c(6:55, 57:70)], 
    y = data_qca$TALKPART[c(6:55, 57:70)], 
    words = data_qca$cases[c(6:55, 57:70)], 
    xlim = c(0, 1), ylim = c(0, 1), 
    xlab="Open Governance Norm", ylab="Participation Talk")
 polygon(x=c(0, 0.5, 0.5, 0), y=c(0.5, 0.5, 1, 1))
 abline(0, 1)
```



```{r}
## sufficient conditions without nc og.norm
tt <- truthTable(data_qca[c(6:55, 57:70), c(18, 10:16)], 
            outcome = c("TALKPART"), incl.cut1=1, sort.by="incl", 
            show.cases = TRUE)
eqmcc(tt, include="?", show.cases = TRUE, details = TRUE, 
            dir.exp = c(rep(1, 7)))
# neg. outcome, to check for contradictions
tt <- truthTable(data_qca[c(6:55, 57:70), c(18, 10:16)], 
            outcome = c("TALKPART"), incl.cut1=1, sort.by="incl", 
            show.cases = TRUE, neg.out = T)
eqmcc(tt, include="?", show.cases = TRUE, details = TRUE)
```


```{r talk_part_sc, echo=FALSE, eval = F}
sc.plot.x <- fsor(fsand(data_qca$RB.Budget, fsnot(data_qca$RB.Complexity)), fsand(data_qca$RB.Complexity, data_qca$NB.visibility.all, data_qca$NB.gov.depth, data_qca$NB.dem.mem))[c(6:55, 57:70)]
sc.plot.y <- data_qca$TALKPART[c(6:55, 57:70)]
sc.plot.w <- data_qca$cases[c(6:55, 57:70)]

textplot(x = sc.plot.x, y = sc.plot.y, words = sc.plot.w, xlim = c(0, 1), ylim = c(0, 1), ylab="Participation Talk", xlab="Set of Sufficient Conditions")
polygon(x=c(0.5, 0.5, 1, 1), y=c(0, 0.5, 0.5, 0))
abline(0, 1)
```


## Transparency Talk
```{r, eval = T}
data_qca$TALKTRANS <- data_qca$TALK.Trans # for QCA package conventions
tt <- truthTable(data_qca[c(1:55, 57:70), c(19, 10:17)], 
            outcome = c("TALKTRANS"), incl.cut1=1, sort.by="incl", 
            show.cases = TRUE)
# necessary conditions
superSubset(data_qca[c(1:55, 57:60), c(19, 10:17)], outcome = "TALKTRANS", 
            relation="nec", incl.cut=0.9, cov.cut=0.76) 
# neg. outcome, to check for contradictions
superSubset(data_qca[c(1:55, 57:60), c(19, 10:17)], outcome = "TALKTRANS", 
            relation="nec", incl.cut=0.9, cov.cut=0.76, neg.out = T) 
```

```{r talk_trans_nc, echo=FALSE, eval = F}
textplot(x = data_qca$NB.og.norm[c(1:55, 57:70)], y = data_qca$TALKTRANS[c(1:55, 57:70)], words = data_qca$cases[c(1:55, 57:70)], xlim = c(0, 1), ylim = c(0, 1), xlab="Open Governance Norm", ylab="Transparency Talk")
polygon(x=c(0, 0.5, 0.5, 0), y=c(0.5, 0.5, 1, 1))
abline(0, 1)
```

```{r, eval=T}
# sufficient conditions, w/o og. norm
tt <- truthTable(data_qca[c(1:55, 57:70), c(19, 10:16)], 
            outcome = c("TALKTRANS"), incl.cut1=1, sort.by="incl", 
            show.cases = TRUE)
eqmcc(tt, include="?", show.cases = TRUE, details = TRUE,
            dir.exp = c(rep(1, 7)))
# neg. outcome, to check for contradictions
tt <- truthTable(data_qca[c(1:55, 57:70), c(19, 10:16)], 
            outcome = c("TALKTRANS"), incl.cut1=0.8, sort.by="incl", 
            show.cases = TRUE, neg.out = T)
eqmcc(tt, include="?", show.cases = TRUE, details = TRUE)
```

```{r talk_trans_sc,  echo=FALSE, eval = F}
sc.plot.x <- fsor(fsand(data_qca$RB.Budget, fsnot(data_qca$RB.Complexity)), fsand(data_qca$RB.Complexity, data_qca$NB.visibility.all, data_qca$NB.gov.depth, data_qca$NB.dem.mem))[c(1:55, 57:70)]
sc.plot.y <- data_qca$TALKTRANS[c(1:55, 57:70)]
sc.plot.w <- data_qca$cases[c(1:55, 57:70)]

textplot(x = sc.plot.x, y = sc.plot.y, words = sc.plot.w, xlim = c(0, 1), ylim = c(0, 1), ylab="Transparency Talk", xlab="Set of Sufficient Conditions")
polygon(x=c(0.5, 0.5, 1, 1), y=c(0, 0.5, 0.5, 0))
abline(0, 1)
```

## Combined Talk
```{r talk}
#truth table
data_qca$TALK <- fsor(data_qca$TALK.Part, 
            data_qca$TALK.Trans) # for QCA package conventions

tt <- truthTable(data_qca[c(20, 10:11, 13:17)], outcome = 
            c("TALK"), incl.cut1=1, sort.by="incl", 
            show.cases = TRUE)

# necessary conditions for participation talk
superSubset(data_qca[c(20, 10:17)], outcome = 
            "TALK", relation="necessity", incl.cut=0.8, cov.cut=0.8)
# neg. outcome, to check for contradictions
superSubset(data_qca[c(20, 10:17)], outcome = 
            "TALK", relation="necessity", incl.cut=0.8, cov.cut=0.8,
            neg.out = T)
```

```{r talk_nc, echo=F}
textplot(x = data_qca$NB.og.norm, 
    y = data_qca$TALK, 
    words = data_qca$cases,
    xlim = c(0, 1), ylim = c(0, 1), 
    xlab="Open Governance Norm", ylab="Talk")
 polygon(x=c(0, 0.5, 0.5, 0), y=c(0.5, 0.5, 1, 1))
 abline(0, 1)
```

```{r talk_nc_venn, echo = F}
nc_talk <- superSubset(data_qca[c(20, 10:17)], outcome = 
            "TALK", relation="necessity", incl.cut=0.8, cov.cut=0.8)
nc_talk <- nc_talk$coms

venn <- venn.diagram(
x = list(
 "TALK" = which(data_qca$TALK == 1),
 "OG.NORM" = which(nc_talk[ , 1] == 1)),
filename = NULL,
scaled = T,
 fill = gray(c(0.9, 0.5))
 )
 grid.draw(venn)
```


```{r, eval = T}
## sufficient conditions without nc og.norm
tt <- truthTable(data_qca[c(20, 10:11, 13:16)], 
            outcome = c("TALK"), incl.cut1=1, sort.by="incl", 
            show.cases = TRUE)
# conservative solution
eqmcc(tt, show.cases = TRUE, details = TRUE)

# intermediary solution
intermed.sol <- eqmcc(tt, include="?", show.cases = TRUE, details = TRUE, 
            dir.exp = c(rep(1, 6)))
intermed.sol
# parsimonious solution
eqmcc(tt, include="?", show.cases = TRUE, details = TRUE)
# neg. outcome, to check for contradictions
tt <- truthTable(data_qca[c(20, 10:11, 13:16)], 
            outcome = c("TALK"), incl.cut1=1, sort.by="incl", 
            show.cases = TRUE, neg.out = T)
sc <- eqmcc(tt, include="?", show.cases = TRUE, details = TRUE, 
            dir.exp = c(rep(1, 6)))

sc$i.sol$C1P1$IC
```


```{r talk_sc, echo=FALSE, eval = T}
sc.plot.x <- fsor(fsand(data_qca$RB.Budget, data_qca$RB.Inequality),
                  fsand(data_qca$RB.Inequality, data_qca$NB.dem.mem),
                  fsand(data_qca$NB.visibility.all, data_qca$NB.dem.mem, data_qca$NB.gov.depth))
sc.plot.y <- data_qca$TALK
sc.plot.w <- data_qca$cases

textplot(x = sc.plot.x, y = sc.plot.y, words = sc.plot.w, xlim = c(0, 1), ylim = c(0, 1), ylab="Participation Talk", xlab="Set of Sufficient Conditions")
polygon(x=c(0.5, 0.5, 1, 1), y=c(0, 0.5, 0.5, 0))
abline(0, 1)
```


```{r talk_sc_venn, echo = F}
PIms <- intermed.sol$i.sol$C1P1$pims
library(VennDiagram)
venn <- venn.diagram(x = list(
"TALK" = which(data_qca$TALK == 1),
"BUDG*INEQ" = which(PIms[ , 1] == 1),
"INEQ*DEM.MEM" = which(PIms[ , 2] == 1),
"VIS*GOV*DEM.MEM" = which(PIms[ , 3] == 1)),
filename = NULL,
fill = gray(c(0.3, 0.5, 0.7, 0.9))
)

grid.draw(venn)
```


## Participation Decision
```{r, eval = T}
data_qca$DECPART <- data_qca$DEC.Part # for QCA package conventions

tt <- truthTable(data_qca[c(21, 10:17)], 
            outcome = c("DECPART"), incl.cut1=1, sort.by="incl", 
            show.cases = TRUE)
superSubset(data_qca[c(21, 10:17)], outcome = "DECPART", 
            relation="nec", incl.cut=0.6, cov.cut=0.7) 
# neg. outcome, to check for contradictions
superSubset(data_qca[c(21, 10:17)], outcome = "DECPART", 
            relation="nec", incl.cut=0.8, cov.cut=0.9, neg.out = T) 
# sufficient conditions
eqmcc(tt, include="?", show.cases = TRUE, details = TRUE,
            dir.exp = c(rep(1, 8)))
# neg. outcome, to check for contradictions
tt <- truthTable(data_qca[c(1:15, 20:70), c(21, 10:17)], 
            outcome = c("DECPART"), incl.cut1=1, sort.by="incl", 
            show.cases = TRUE, neg.out = T)
eqmcc(tt, include="?", show.cases = TRUE, details = TRUE, 
            dir.exp = c(rep(1, 8)))
```

```{r part_dec_sc, echo=FALSE, eval = F}
sc.plot.x <- fsand(fsnot(data_qca$NB.dem.mem[c(1:15, 20:70)]), data_qca$RB.Inequality[c(1:15, 20:70)])
sc.plot.y <- data_qca$DECPART[c(1:15, 20:70)]
sc.plot.w <- data_qca$cases[c(1:15, 20:70)]

textplot(x = sc.plot.x, y = sc.plot.y, words = sc.plot.w, xlim = c(0, 1), ylim = c(0, 1), ylab="Participation Decisions", xlab="Set of Sufficient Conditions")
polygon(x=c(0.5, 0.5, 1, 1), y=c(0, 0.5, 0.5, 0))
abline(0, 1)
```


## Transparency Decision
```{r, eval = T}
data_qca$DECTRANS <- data_qca$DEC.Trans # for QCA package conventions
tt <- truthTable(data_qca[c(1:55, 57:70), c(22, 10:17)], 
            outcome = c("DECTRANS"), incl.cut1=1, sort.by="incl", 
            show.cases = TRUE)
# necessary conditions
superSubset(data_qca[c(1:55, 57:70), c(22, 10:17)], outcome = "DECTRANS", 
            relation="nec", incl.cut=0.9, cov.cut=0.8) 
# neg. outcome, to check for contradictions
superSubset(data_qca[c(1:55, 57:70), c(22, 10:17)], outcome = "DECTRANS", 
            relation="nec", incl.cut=0.9, cov.cut=0.8, neg.out = T) 
```

```{r dec_trans_nc, echo=FALSE, eval = F}
textplot(x = data_qca$NB.og.norm[c(1:55, 57:70)], y = data_qca$DECTRANS[c(1:55, 57:70)], words = data_qca$cases[c(1:55, 57:70)], xlim = c(0, 1), ylim = c(0, 1), xlab="Open Governance Norm", ylab="Transparency Decisions")
polygon(x=c(0, 0.5, 0.5, 0), y=c(0.5, 0.5, 1, 1))
abline(0, 1)
```

```{r, eval = T}
# sufficient conditions w/o og.norm
tt <- truthTable(data_qca[c(1:55, 57:70), c(22, 10:16)], 
            outcome = c("DECTRANS"), incl.cut1=1, sort.by="incl", 
            show.cases = TRUE)
eqmcc(tt, include="?", show.cases = TRUE, details = TRUE,
            dir.exp = c(rep(1, 7)))
# neg. outcome, to check for contradictions
tt <- truthTable(data_qca[c(1:55, 57:70), c(22, 10:16)], 
            outcome = c("DECTRANS"), incl.cut1=0.8, sort.by="incl", 
            show.cases = TRUE, neg.out = T)
eqmcc(tt, include="?", show.cases = TRUE, details = TRUE,
            dir.exp = c(rep(1, 7)))

```

```{r dec_trans_sc, echo=FALSE, eval = F}
sc.plot.x <- fsor(data_qca$NB.dem.mem, data_qca$NB.visibility.hl, data_qca$RB.Inequality)
sc.plot.y <- data_qca$DECTRANS
sc.plot.w <- data_qca$cases

textplot(x = sc.plot.x[c(1:55, 57:70)], y = sc.plot.y[c(1:55, 57:70)], words = sc.plot.w[c(1:55, 57:70)], xlim = c(0, 1), ylim = c(0, 1), ylab="Transparency Decisions", xlab="Set of Sufficient Conditions")
polygon(x=c(0.5, 0.5, 1, 1), y=c(0, 0.5, 0.5, 0))
abline(0, 1)
```

## Combined Decision
```{r DEC, eval = T}
data_qca$DECISION <- fsor(data_qca$DEC.Part, data_qca$DEC.Trans)

tt <- truthTable(data_qca[c(23, 10:11, 13:17)], outcome = c("DECISION"), 
            incl.cut1=1, sort.by="incl", show.cases = TRUE)
# necessary conditions
superSubset(data_qca[c(23, 10:11, 13:17)], outcome = "DECISION", 
            relation="nec", incl.cut=0.8, cov.cut=0.5)
# neg. outcome, to check for contradictions
superSubset(data_qca[c(23, 10:11, 13:17)], outcome = "DECISION", 
            relation="nec", incl.cut=0.8, cov.cut=0.878, 
            neg.out = T)
```

```{r decision_nc, echo=FALSE, eval = T}
textplot(x = data_qca$NB.og.norm, 
         y = data_qca$DECISION, 
         words = data_qca$cases, 
         xlim = c(0, 1), ylim = c(0, 1), 
         xlab="Open Governance Norm", 
         ylab="Transparency Decisions")
polygon(x=c(0, 0.5, 0.5, 0), y=c(0.5, 0.5, 1, 1))
abline(0, 1)
```


```{r dec_nc_venn, echo = F}
nc_dec <- superSubset(data_qca[c(23, 10:11, 13:17)], outcome = "DECISION", 
            relation="nec", incl.cut=0.8, cov.cut=0.5)
nc_dec <- nc_dec$coms

venn <- venn.diagram(
x = list(
 "DECISION" = which(data_qca$DECISION == 1),
 "OG.NORM" = which(nc_dec[ , 1] == 1)),
filename = NULL,
scaled = T,
 fill = gray(c(0.9, 0.5))
 )
 grid.draw(venn)
```

```{r, eval = T}
# sufficient conditions, w/o OG.Norm
tt <- truthTable(data_qca[c(23, 10:11, 13:16)], outcome = c("DECISION"), 
            incl.cut1=1, sort.by="incl", show.cases = TRUE)

# conservative
eqmcc(tt, show.cases = TRUE, details = TRUE)

# intermediate
intermed.sol <- eqmcc(tt, include="?", show.cases = TRUE, details = TRUE,
            dir.exp = c(rep(1, 6)))
intermed.sol
# parsimonious
eqmcc(tt, include="?", show.cases = TRUE, details = TRUE)

#factorize(sc)
# neg. outcome, to check for contradictions
tt <- truthTable(data_qca[c(23, 10:11, 13:17)], outcome = c("DECISION"), 
            incl.cut1=1, sort.by="incl", show.cases = TRUE,
            neg.out = T)
eqmcc(tt, include="?", show.cases = TRUE, details = TRUE)
```


```{r dec_sc, echo=FALSE, eval = T}
sc.plot.x <- fsor(data_qca$RB.Inequality, 
                  fsand(data_qca$NB.visibility.all, data_qca$NB.gov.depth,
                        data_qca$NB.dem.mem))
sc.plot.y <- data_qca$DECISION
sc.plot.w <- data_qca$cases

textplot(x = sc.plot.x, y = sc.plot.y, words = sc.plot.w, xlim = c(0, 1), ylim = c(0, 1), ylab="Transparency Decisions", xlab="Set of Sufficient Conditions")
polygon(x=c(0.5, 0.5, 1, 1), y=c(0, 0.5, 0.5, 0))
abline(0, 1)
```

```{r dec_sc_venn, echo = F}
PIms <- intermed.sol$i.sol$C1P1$pims
library(VennDiagram)
venn <- venn.diagram(x = list(
"DECISION" = which(data_qca$DECISION == 1),
"INEQ" = which(PIms[ , 1] == 1),
"VIS*GOV.DEPTH*DEM.MEM" = which(PIms[ , 2] == 1)),
filename = NULL,
fill = gray(c(0.9, 0.5, 0.7))
)

grid.draw(venn)
```

## Participation Action: No. of NGOs

```{r, eval = T}
data_qca$ACTPART1 <- data_qca$ACT.Part.1 # for QCA package conventions
tt <- truthTable(data_qca[c(24, 10:17)], outcome = c("ACTPART1"), 
            incl.cut1=1, sort.by="incl", show.cases = TRUE)
# necessary conditions
superSubset(data_qca[c(24, 10:17)], outcome = "ACTPART1", 
            relation="nec", incl.cut=0.8, cov.cut=0.6) 
# neg. outcome, to check for contradictions
superSubset(data_qca[c(24, 10:17)], outcome = "ACTPART1", 
            relation="nec", incl.cut=0.9, cov.cut=0.6, neg.out = T) 
# sufficient conditions
eqmcc(tt, include="?", show.cases = TRUE, details = TRUE,
            dir.exp = c(rep(1, 8)))

# neg. outcome, to check for contradictions
tt <- truthTable(data_qca[c(24, 10:17)], outcome = c("ACTPART1"), 
            incl.cut1=1, sort.by="incl", show.cases = TRUE, 
            neg.out = T)
sc <- eqmcc(tt, include="?", show.cases = TRUE, details = TRUE)
sc$essential
```


```{r act_part_ngos1_sc, echo=FALSE, eval = F}
sc.plot.x <- fsand(data_qca$NB.dem.mem, fsor(data_qca$RB.Budget, 
            data_qca$NB.gov.depth, data_qca$NB.visibility.all))
sc.plot.y <- data_qca$ACTPART1
sc.plot.w <- data_qca$cases

textplot(x = sc.plot.x, y = sc.plot.y, words = sc.plot.w, xlim = c(0, 1), ylim = c(0, 1), ylab="Participation Action, NGOs", xlab="Set of Sufficient Conditions")
polygon(x=c(0.5, 0.5, 1, 1), y=c(0, 0.5, 0.5, 0))
abline(0, 1)
```



## Participation Action: No. of NGO representatives
```{r, eval = T}
data_qca$ACTPART2 <- data_qca$ACT.Part.2 # for QCA package conventions
tt <- truthTable(data_qca[c(25, 10:17)], outcome = c("ACTPART2"), 
            incl.cut1=1, sort.by="incl", show.cases = TRUE)
# necessary conditions
superSubset(data_qca[c(25, 10:17)], outcome = "ACTPART2", 
            relation="nec", incl.cut=0.8, cov.cut=0.5)
# neg. outcome, to check for contradictions
superSubset(data_qca[c(25, 10:17)], outcome = "ACTPART2", 
            relation="nec", incl.cut=0.8, cov.cut=0.92, 
            neg.out = T)
# sufficient conditions
eqmcc(tt, include="?", show.cases = TRUE, details = TRUE,
            dir.exp = c(rep(1, 8)))
# neg. outcome, to check for contradictions
tt <- truthTable(data_qca[c(25, 10:17)], outcome = c("ACTPART2"), 
            incl.cut1=1, sort.by="incl", show.cases = TRUE,
            neg.out = T)
sc <- eqmcc(tt, include="?", show.cases = TRUE, details = TRUE)
sc$essential
```

## Participation Action: Participation events

```{r ACT.Part.4, eval=T, eval = T}
data_qca$ACTPART4 <- data_qca$ACT.Part.4 # for QCA package conventions
tt <- truthTable(data_qca[c(26, 10:17)], outcome = c("ACTPART4"), 
            incl.cut1=1, sort.by="incl", show.cases = TRUE)
# necessary conditions
superSubset(data_qca[c(26, 10:17)], outcome = "ACTPART4", 
            relation="nec", incl.cut=0.9, cov.cut=0.7) 
# neg. outcome, to check for contradictions
superSubset(data_qca[c(26, 10:17)], outcome = "ACTPART4", 
            relation="nec", incl.cut=0.9, cov.cut=0.63,
            neg.out = T)
```

```{r act_part_events, echo=FALSE, eval = F}
nc.x <- fsor(data_qca$RB.Budget, data_qca$NB.visibility.all, data_qca$NB.dem.mem)
textplot(x = nc.x, y = data_qca$ACTPART4, words = data_qca$cases, xlim = c(0, 1), ylim = c(0, 1), xlab="Set of functionally equivalent necessary conditions", ylab="Participation events")
polygon(x=c(0, 0.5, 0.5, 0), y=c(0.5, 0.5, 1, 1))
abline(0, 1)
```

```{r, eval = T}
# sufficient conditions
tt <- truthTable(data_qca[c(26, 10:17)], outcome = c("ACTPART4"), 
            incl.cut1=0.8, sort.by="incl", show.cases = TRUE)
# use parsimonious solution here. 
sc <- eqmcc(tt, include="?", show.cases = TRUE, details = TRUE)
sc$essential
# neg. outcome, to check for contradictions
tt <- truthTable(data_qca[c(26, 10:17)], outcome = c("ACTPART4"), 
            incl.cut1=1, sort.by="incl", show.cases = TRUE, 
            neg.out = T)
eqmcc(tt, include="?", show.cases = TRUE, details = TRUE,
            dir.exp = c(rep(1, 8)))
```

## Participation Action
```{r act_part_all, eval = T}
data_qca$ACTPART <- fsor(data_qca$ACTPART1, 
            data_qca$ACTPART2, data_qca$ACTPART4)
tt <- truthTable(data_qca[c(27, 10:11, 13:17)], 
            outcome = c("ACTPART"), incl.cut1=1, sort.by="incl", 
            show.cases = TRUE)
# necessary conditions
superSubset(data_qca[c(27, 10:11, 13:17)], outcome = "ACTPART", 
            relation="nec", incl.cut=1, cov.cut=0.6) 
# neg. outcome, to check for contradictions
superSubset(data_qca[c(27, 10:11, 13:17)], outcome = "ACTPART", 
            relation="nec", incl.cut=0.9, cov.cut=0.4, neg.out = T) 
# conservative solution
sc <- eqmcc(tt, show.cases = T, details = T)
sc$essential
# intermed
intermed.sol <- eqmcc(tt, include="?", show.cases = TRUE, details = TRUE,
            dir.exp = c(rep(1, 7)))
intermed.sol
eqmcc(tt, include="?", show.cases = TRUE, details = TRUE)
```

```{r act_part_sc, echo=FALSE, eval = T}
sc.plot.x <- fsor(data_qca$NB.visibility.all,
                  fsand(data_qca$RB.Budget, fsnot(data_qca$RB.Inequality)),
                  fsand(data_qca$RB.Budget, data_qca$NB.dem.mem, data_qca$NB.og.norm))
sc.plot.y <- data_qca$ACTPART
sc.plot.w <- data_qca$cases

textplot(x = sc.plot.x, y = sc.plot.y, words = sc.plot.w, xlim = c(0, 1), ylim = c(0, 1), ylab="Participation Action", xlab="Set of Sufficient Conditions")
polygon(x=c(0.5, 0.5, 1, 1), y=c(0, 0.5, 0.5, 0))
abline(0, 1)
```

```{r actpart_all_venn, echo = F}
PIms <- intermed.sol$i.sol$C1P1$pims
library(VennDiagram)
venn <- venn.diagram(x = list(
"PART.ACT" = which(data_qca$ACTPART == 1),
"VIS" = which(PIms[ , 1] == 1),
"BUDG*og.norm" = which(PIms[ , 2] == 1),
"BUDG*INEQ*DEM.MEM" = which(PIms[ , 3] == 1)),
filename = NULL,
fill = gray(c(0.3, 0.5, 0.7, 0.9))
)

grid.draw(venn)
```

## Transparency Action

```{r, eval = T}
data_qca$ACTTRANS <- data_qca$ACT.Trans # for QCA package conventions
tt <- truthTable(data_qca[c(28, 10:11, 13:17)], 
            outcome = c("ACTTRANS"), incl.cut1=0.8, sort.by="incl", 
            show.cases = TRUE)
# necessary conditions
superSubset(data_qca[c(28, 10:11, 13:17)], outcome = "ACTTRANS", 
            relation="nec", incl.cut=0.8, cov.cut=0.37) 
# neg. outcome, to check for contradictions
superSubset(data_qca[c(28, 10:11, 13:17)], outcome = "ACTTRANS", 
            relation="nec", incl.cut=1, cov.cut=0.4, neg.out = T) 
```

```{r transp_act_nc, echo=FALSE, eval = T}
textplot(x = data_qca$NB.dem.mem, y = data_qca$ACTTRANS, words = data_qca$cases, xlim = c(0, 1), ylim = c(0, 1), xlab="Presence of Democratic Members", ylab="Transparency Action")
polygon(x=c(0, 0.5, 0.5, 0), y=c(0.5, 0.5, 1, 1))
abline(0, 1)
```

```{r transp_act_nc2, echo=FALSE, eval = T}
textplot(x = data_qca$NB.og.norm, y = data_qca$ACTTRANS, words = data_qca$cases, xlim = c(0, 1), ylim = c(0, 1), xlab="Presence of Governance Norm", ylab="Transparency Action")
polygon(x=c(0, 0.5, 0.5, 0), y=c(0.5, 0.5, 1, 1))
abline(0, 1)
```

```{r transp_act_all_nc_venn, echo = F}
nc_transpart <- superSubset(data_qca[c(28, 10:11, 13:17)], outcome = "ACTTRANS", 
            relation="nec", incl.cut=0.8, cov.cut=0.37) 
nc_transpart <- nc_transpart$coms

venn <- venn.diagram(
x = list(
"ACT.TRANSP" = which(data_qca$ACTTRANS == 1),
"OG.NORM" = which(nc_transpart[ , 1] == 1),
"DEM.MEM" = which(nc_transpart[ , 2] == 1)),
filename = NULL,
scaled = T,
 fill = gray(c(0.9, 0.5, 0.3))
 )
 grid.draw(venn)
```

```{r, eval = T}
#sufficient condition, without democratic members
tt <- truthTable(data_qca[c(28, 10:11, 13:15, 17)], 
            outcome = c("ACTTRANS"), incl.cut1=1, sort.by="incl", 
            show.cases = TRUE)
eqmcc(tt, show.cases = TRUE, details = TRUE)
eqmcc(tt, include="?", show.cases = TRUE, details = TRUE,
            dir.exp = c(rep(1, 6)))
sc <- eqmcc(tt, include="?", show.cases = TRUE, details = TRUE)
sc$solution
# neg. outcome, to check for contradictions
tt <- truthTable(data_qca[c(28, 10:11, 13:15, 17)], 
            outcome = c("ACTTRANS"), incl.cut1=1, sort.by="incl", 
            show.cases = TRUE, neg.out = T)
eqmcc(tt, include="?", show.cases = TRUE, details = TRUE, 
            dir.exp = c(rep(1, 6)))
```



```{r export, echo = F}
write.csv2(data_qca, file = "data_qca.csv")
```

