---
output:
  html_document: default
  pdf_document:
    fig_crop: no
    keep_tex: yes
---

```{r echo=FALSE}
library(knitr)
opts_chunk$set(cache=F, autodep=TRUE, out.width = "\\textwidth", fig.height = 6, fig.width = 8,  dpi = 300, warning=F, message=F, dev = "png")
```

In the following appendix, I present the `R Code` for an alternative, fuzzy-set
calibration of the data.

First, I load the required R packages[^1]:
```{r setup, message=FALSE}
library(QCA)
library(QCA3)
library(wordcloud)
library(SetMethods)
library(car)
```

[^1]: Dusa, Adrian and Alrik Thiem (2014). QCA: A Package for Qualitative Comparative Analysis. R package version 1.1-3. URL: http://cran.r-project.org/package=QCA.
Fellows, Ian (2014). wordcloud: Word Clouds. R package version 2.5. URL: http://CRAN.R-project.org/package=wordcloud.
Fox, John and Sanford Weisberg (2011). An {R} Companion to Applied Regression,  Second Edition. Thousand Oaks CA: Sage. URL: http://socserv.socsci.mcmaster.ca/jfox/Books/Companion.
Huang, Ronggui. (2014). QCA3: Yet another package for Qualitative Comparative Analysis. R package version 0.0-7. URL: http://asrr.r-forge.r-project.org/.
Quaranta, Mario  (2013). SetMethods: A Package Companion to "Set-Theoretic Methods for the Social Sciences". R package version 1.0. URL: http://CRAN.R-project.org/package=SetMethods.


Next, I import the raw data and create an empty data-set for the QCA data-set:
```{r import}
data <- read.csv("../data/raw-data.csv")
data$X <- NULL # clean up import artifact
data$cases <-  paste(data$IO, data$Year, sep = "") # name cases
data_qca <- as.data.frame(matrix(0, ncol = 0, nrow = 70))
data_qca$cases <- data$cases
# add case names as row names
row.names(data_qca) <- data_qca$cases
```



#Calibration
The following code-blocks show the steps I took to calibrate the data-set. Again, 
the detailed description is included in Chapter 5.

##Talk
```{r}
thr1 <- 0.8
data_qca$TALK.Part <- c(thr1, 1, 1, thr1, thr1, rep(0, 31), rep(thr1, 5),
            1,thr1, rep(1, 3), rep(thr1, 3), 1, rep(thr1, 4), 1, 0, 1, 1, 
            rep(thr1, 10), 1, 1)
data_qca$TALK.Trans <- c(rep(0, 36), rep(thr1, 9), 1, rep(thr1, 8), 1, 0, 
            rep(thr1, 2), 1, thr1, thr1, 1, rep(thr1, 7), 1)
```

## Decision
```{r}
thr1 <- 0.7
thr2 <- 0.9
data_qca$DEC.Part <- c(rep(0, 15), rep(1, 4), rep(0, 36), rep(1, 7), 
            rep(0,8))

data_qca$DEC.Trans <- c(rep(0, 29), rep(thr1, 7), rep(thr2, 7), 
            rep(1, 12), 0, thr1, rep(thr2, 11), rep(1, 2))
```

## Action
```{r}
data_qca$ACT.Part.1 <-  c(0, rep(1, 7), rep(0, 26), rep(1, 21), rep(1, 4), 
            rep(0, 8), rep(1, 3))
data_qca$ACT.Part.2 <-  c(rep(0, 51), rep(1, 4), rep(0, 12), rep(1, 3))
data_qca$ACT.Part.4 <-  c(rep(0, 25), rep(1, 13), rep(0, 3), rep(1, 5), 
            rep(0, 2), rep(1, 7), rep(0, 7), rep(1, 3),0, 0, 1, 1, 1)
data_qca$ACT.Trans <- c(rep(0, 4), rep(1, 3), rep(0, 38), rep(1, 10),
            rep(0, 7), rep(1, 4), rep(0, 4))
```

## Resource-based conditions
```{r}
thr1 <- 0.8
data_qca$RB.Budget <-  c(rep(0, 26), rep(thr1, 4), rep(0, 6), rep(thr1, 9), 
            rep(0, 10), rep(0, 2), rep(1, 4), rep(0, 6), rep(thr1, 3))
data_qca$RB.Inequality <-  recode(data$RB.Inequality, 
            recodes = "0:0.8126000=0; 0.8126313:0.9=1")
data_qca$RB.Complexity <- c(rep(1, 55), rep(0, 15))
```

## Norm-based conditions
```{r}
thr1 <- 0.8
data_qca$NB.visibility.all <-  c(rep(0, 29), rep(thr1, 5), rep(1, 4), 
            rep(thr1, 7), rep(1, 6), rep(thr1, 3), 1, rep(0, 15))
data_qca$NB.visibility.hl <-  c(rep(0, 29), rep(1, 3), rep(0, 10), 
            rep(1, 5), rep(0, 5), rep(1, 3), rep(0, 15))
data_qca$NB.gov.depth <- c(rep(0, 13), rep(thr1, 21), rep(1, 21), rep(0, 15))
data_qca$NB.dem.mem <-  c(rep(0, 36), rep(1, 19), rep(0, 7), rep(1, 8))
data_qca$NB.og.norm <-  c(rep(0, 33), rep(thr1, 6), rep(1, 16), rep(1, 15))

```

# QCA analyses
Next, I present the analysis of the individual outcome variables. 

## Participation Talk
```{r part_talk}
#truth table w/o IAEA1957:1961, OPCW 1997
data_qca$TALKPART <- data_qca$TALK.Part # for QCA package conventions
tt <- truthTable(data_qca[c(6:55, 57:70), c(18, 10:17)], outcome = 
            c("TALKPART"), incl.cut1=0.8, sort.by="incl", 
            show.cases = TRUE)

# necessary conditions for participation talk
superSubset(data_qca[c(6:55, 57:70), c(18, 10:17)], outcome = 
            "TALKPART", relation="necessity", incl.cut=1, cov.cut=0.8)
# neg. outcome, to check for contradictions
superSubset(data_qca[c(6:55, 57:70), c(18, 10:17)], outcome = 
            "TALKPART", relation="necessity", incl.cut=0.9, cov.cut=0.8, neg.out = T)
```

```{r talk_part_nc, echo=FALSE}
textplot(x = data_qca$NB.og.norm[c(6:55, 57:70)], 
    y = data_qca$TALKPART[c(6:55, 57:70)], 
    words = data_qca$cases[c(6:55, 57:70)], 
    xlim = c(0, 1), ylim = c(0, 1), 
    xlab="Open Governance Norm", ylab="Participation Talk")
 polygon(x=c(0, 0.5, 0.5, 0), y=c(0.5, 0.5, 1, 1))
 abline(0, 1)
```

```{r}
## sufficient conditions without nc og.norm
tt <- truthTable(data_qca[c(6:55, 57:70), c(18, 10:16)], 
            outcome = c("TALKPART"), incl.cut1=0.8, sort.by="incl", 
            show.cases = TRUE)
eqmcc(tt, include="?", show.cases = TRUE, details = TRUE)
# neg. outcome, to check for contradictions
tt <- truthTable(data_qca[c(6:55, 57:70), c(18, 10:16)], 
            outcome = c("TALKPART"), incl.cut1=0.8, sort.by="incl", 
            show.cases = TRUE, neg.out = T)
eqmcc(tt, include="?", show.cases = TRUE, details = TRUE)
# exclude complexity, because it is redundant
```

```{r talk_part_sc, echo=FALSE}
sc.plot.x <- fsor(data_qca$NB.dem.mem, data_qca$RB.Inequality)[c(6:55, 57:70)]
sc.plot.y <- data_qca$TALKPART[c(6:55, 57:70)]
sc.plot.w <- data_qca$cases[c(6:55, 57:70)]

textplot(x = sc.plot.x, y = sc.plot.y, words = sc.plot.w, xlim = c(0, 1), ylim = c(0, 1), ylab="Participation Talk", xlab="Set of Sufficient Conditions")
polygon(x=c(0.5, 0.5, 1, 1), y=c(0, 0.5, 0.5, 0))
abline(0, 1)
```


## Transparency Talk
```{r}
data_qca$TALKTRANS <- data_qca$TALK.Trans # for QCA package conventions
tt <- truthTable(data_qca[c(1:55, 57:70), c(19, 10:17)], 
            outcome = c("TALKTRANS"), incl.cut1=0.8, sort.by="incl", 
            show.cases = TRUE)
# necessary conditions
superSubset(data_qca[c(1:55, 57:60), c(19, 10:17)], outcome = "TALKTRANS", 
            relation="nec", incl.cut=0.9, cov.cut=0.76) 
# neg. outcome, to check for contradictions
superSubset(data_qca[c(1:55, 57:60), c(19, 10:17)], outcome = "TALKTRANS", 
            relation="nec", incl.cut=0.9, cov.cut=0.76, neg.out = T) 
```

```{r talk_trans_nc, echo=FALSE}
textplot(x = data_qca$NB.og.norm[c(1:55, 57:70)], y = data_qca$TALKTRANS[c(1:55, 57:70)], words = data_qca$cases[c(1:55, 57:70)], xlim = c(0, 1), ylim = c(0, 1), xlab="Open Governance Norm", ylab="Transparency Talk")
polygon(x=c(0, 0.5, 0.5, 0), y=c(0.5, 0.5, 1, 1))
abline(0, 1)
```

```{r, eval=T}
# sufficient conditions, w/o og. norm
tt <- truthTable(data_qca[c(1:55, 57:70), c(19, 10:16)], 
            outcome = c("TALKTRANS"), incl.cut1=0.8, sort.by="incl", 
            show.cases = TRUE)
eqmcc(tt, include="?", show.cases = TRUE, details = TRUE)
# neg. outcome, to check for contradictions
tt <- truthTable(data_qca[c(1:55, 57:70), c(19, 10:16)], 
            outcome = c("TALKTRANS"), incl.cut1=0.8, sort.by="incl", 
            show.cases = TRUE, neg.out = T)
eqmcc(tt, include="?", show.cases = TRUE, details = TRUE)
# exclude complexity, because it is redundant
```

```{r talk_trans_sc,  echo=FALSE}
sc.plot.x <- fsor(data_qca$NB.dem.mem, data_qca$RB.Inequality)[c(1:55, 57:60)]
sc.plot.y <- data_qca$TALKTRANS[c(1:55, 57:60)]
sc.plot.w <- data_qca$cases[c(1:55, 57:60)]

textplot(x = sc.plot.x, y = sc.plot.y, words = sc.plot.w, xlim = c(0, 1), ylim = c(0, 1), ylab="Transparency Talk", xlab="Set of Sufficient Conditions")
polygon(x=c(0.5, 0.5, 1, 1), y=c(0, 0.5, 0.5, 0))
abline(0, 1)
```

## Participation Decision
```{r}
data_qca$DECPART <- data_qca$DEC.Part # for QCA package conventions
# without IAEA1972:1975
tt <- truthTable(data_qca[c(1:15, 20:70), c(20, 10:17)], 
            outcome = c("DECPART"), incl.cut1=1, sort.by="incl", 
            show.cases = TRUE)
superSubset(data_qca[c(1:15, 20:70), c(20, 10:17)], outcome = "DECPART", 
            relation="nec", incl.cut=1, cov.cut=1) 
# neg. outcome, to check for contradictions
superSubset(data_qca[c(1:15, 20:70), c(20, 10:17)], outcome = "DECPART", 
            relation="nec", incl.cut=1, cov.cut=1, neg.out = T) 
# sufficient conditions
eqmcc(tt, include="?", show.cases = TRUE, details = TRUE)
QCAfit(fsand(fsnot(data_qca$NB.dem.mem[c(1:15, 20:70)]), 
             data_qca$RB.Inequality[c(1:15, 20:70)]), 
             data_qca$DECPART[c(1:15, 20:70)])
# neg. outcome, to check for contradictions
tt <- truthTable(data_qca[c(1:15, 20:70), c(20, 10:17)], 
            outcome = c("DECPART"), incl.cut1=1, sort.by="incl", 
            show.cases = TRUE, neg.out = T)
eqmcc(tt, include="?", show.cases = TRUE, details = TRUE)
```

```{r part_dec_sc, echo=FALSE}
sc.plot.x <- fsand(fsnot(data_qca$NB.dem.mem[c(1:15, 20:70)]), data_qca$RB.Inequality[c(1:15, 20:70)])
sc.plot.y <- data_qca$DECPART[c(1:15, 20:70)]
sc.plot.w <- data_qca$cases[c(1:15, 20:70)]

textplot(x = sc.plot.x, y = sc.plot.y, words = sc.plot.w, xlim = c(0, 1), ylim = c(0, 1), ylab="Participation Decisions", xlab="Set of Sufficient Conditions")
polygon(x=c(0.5, 0.5, 1, 1), y=c(0, 0.5, 0.5, 0))
abline(0, 1)
```


## Transparency Decision
```{r}
data_qca$DECTRANS <- data_qca$DEC.Trans # for QCA package conventions
tt <- truthTable(data_qca[c(1:55, 57:70), c(21, 10:17)], 
            outcome = c("DECTRANS"), incl.cut1=0.8, sort.by="incl", 
            show.cases = TRUE)
# necessary conditions
superSubset(data_qca[c(1:55, 57:70), c(21, 10:17)], outcome = "DECTRANS", 
            relation="nec", incl.cut=0.9, cov.cut=0.92) 
# neg. outcome, to check for contradictions
superSubset(data_qca[c(1:55, 57:70), c(21, 10:17)], outcome = "DECTRANS", 
            relation="nec", incl.cut=0.9, cov.cut=1, neg.out = T) 
```

```{r dec_trans_nc, echo=FALSE}
textplot(x = data_qca$NB.og.norm[c(1:55, 57:70)], y = data_qca$DECTRANS[c(1:55, 57:70)], words = data_qca$cases[c(1:55, 57:70)], xlim = c(0, 1), ylim = c(0, 1), xlab="Open Governance Norm", ylab="Transparency Decisions")
polygon(x=c(0, 0.5, 0.5, 0), y=c(0.5, 0.5, 1, 1))
abline(0, 1)
```

```{r}
# sufficient conditions w/o og.norm
tt <- truthTable(data_qca[c(1:55, 57:70), c(21, 10:16)], 
            outcome = c("DECTRANS"), incl.cut1=0.8, sort.by="incl", 
            show.cases = TRUE)
eqmcc(tt, include="?", show.cases = TRUE, details = TRUE)
QCAfit(fsor(data_qca$NB.dem.mem, data_qca$NB.visibility.hl, 
            data_qca$RB.Inequality)[c(1:55, 57:70)], 
            data_qca$DECTRANS[c(1:55, 57:70)] )
# neg. outcome, to check for contradictions
tt <- truthTable(data_qca[c(1:55, 57:70), c(21, 10:16)], 
            outcome = c("DECTRANS"), incl.cut1=0.8, sort.by="incl", 
            show.cases = TRUE, neg.out = T)
eqmcc(tt, include="?", show.cases = TRUE, details = TRUE)
```

```{r dec_trans_sc, echo=FALSE}
sc.plot.x <- fsor(data_qca$NB.dem.mem, data_qca$NB.visibility.hl, data_qca$RB.Inequality)
sc.plot.y <- data_qca$DECTRANS
sc.plot.w <- data_qca$cases

textplot(x = sc.plot.x[c(1:55, 57:70)], y = sc.plot.y[c(1:55, 57:70)], words = sc.plot.w[c(1:55, 57:70)], xlim = c(0, 1), ylim = c(0, 1), ylab="Transparency Decisions", xlab="Set of Sufficient Conditions")
polygon(x=c(0.5, 0.5, 1, 1), y=c(0, 0.5, 0.5, 0))
abline(0, 1)
```

## Participation Action: No. of NGOs

```{r}
data_qca$ACTPART1 <- data_qca$ACT.Part.1 # for QCA package conventions
tt <- truthTable(data_qca[c(22, 10:17)], outcome = c("ACTPART1"), 
            incl.cut1=1, sort.by="incl", show.cases = TRUE)
# necessary conditions
superSubset(data_qca[c(22, 10:17)], outcome = "ACTPART1", 
            relation="nec", incl.cut=0.9, cov.cut=0.6) 
# neg. outcome, to check for contradictions
superSubset(data_qca[c(22, 10:17)], outcome = "ACTPART1", 
            relation="nec", incl.cut=0.9, cov.cut=0.6, neg.out = T) 
## low governance depth is contradictory, necessary for OUT and out
# sufficient conditions
sc <- eqmcc(tt, include="?", show.cases = TRUE, details = TRUE)
sc
factorize(sc)
QCAfit(x = fsand(data_qca$NB.dem.mem, fsor(data_qca$RB.Budget, 
            data_qca$NB.gov.depth, data_qca$NB.visibility.all)), 
            y = data_qca$ACTPART1)
# neg. outcome, to check for contradictions
tt <- truthTable(data_qca[c(22, 10:17)], outcome = c("ACTPART1"), 
            incl.cut1=1, sort.by="incl", show.cases = TRUE, 
            neg.out = T)
eqmcc(tt, include="?", show.cases = TRUE, details = TRUE)
```


```{r act_part_ngos1_sc, echo=FALSE}
sc.plot.x <- fsand(data_qca$NB.dem.mem, fsor(data_qca$RB.Budget, 
            data_qca$NB.gov.depth, data_qca$NB.visibility.all))
sc.plot.y <- data_qca$ACTPART1
sc.plot.w <- data_qca$cases

textplot(x = sc.plot.x, y = sc.plot.y, words = sc.plot.w, xlim = c(0, 1), ylim = c(0, 1), ylab="Participation Action, NGOs", xlab="Set of Sufficient Conditions")
polygon(x=c(0.5, 0.5, 1, 1), y=c(0, 0.5, 0.5, 0))
abline(0, 1)
```

## Participation Action: No. of NGO representatives
```{r}
data_qca$ACTPART2 <- data_qca$ACT.Part.2 # for QCA package conventions
tt <- truthTable(data_qca[c(23, 10:17)], outcome = c("ACTPART2"), 
            incl.cut1=1, sort.by="incl", show.cases = TRUE)
# necessary conditions
superSubset(data_qca[c(23, 10:17)], outcome = "ACTPART2", 
            relation="nec", incl.cut=0.8, cov.cut=0.5)
# neg. outcome, to check for contradictions
superSubset(data_qca[c(23, 10:17)], outcome = "ACTPART2", 
            relation="nec", incl.cut=0.8, cov.cut=0.92, 
            neg.out = T)
# sufficient conditions
eqmcc(tt, include="?", show.cases = TRUE, details = TRUE)
# neg. outcome, to check for contradictions
tt <- truthTable(data_qca[c(23, 10:17)], outcome = c("ACTPART2"), 
            incl.cut1=1, sort.by="incl", show.cases = TRUE,
            neg.out = T)
eqmcc(tt, include="?", show.cases = TRUE, details = TRUE)
```

## Participation Action: Participation events

```{r ACT.Part.4, eval=T}
data_qca$ACTPART4 <- data_qca$ACT.Part.4 # for QCA package conventions
tt <- truthTable(data_qca[c(24, 10:17)], outcome = c("ACTPART4"), 
            incl.cut1=0.7, sort.by="incl", show.cases = TRUE)
# necessary conditions
superSubset(data_qca[c(24, 10:17)], outcome = "ACTPART4", 
            relation="nec", incl.cut=0.9, cov.cut=0.7) 
# neg. outcome, to check for contradictions
superSubset(data_qca[c(24, 10:17)], outcome = "ACTPART4", 
            relation="nec", incl.cut=0.9, cov.cut=0.63,
            neg.out = T)
```

```{r act_part_events, echo=FALSE}
nc.x <- fsor(data_qca$RB.Budget, data_qca$NB.visibility.all, data_qca$NB.dem.mem)
textplot(x = nc.x, y = data_qca$ACTPART4, words = data_qca$cases, xlim = c(0, 1), ylim = c(0, 1), xlab="Set of functionally equivalent necessary conditions", ylab="Participation events")
polygon(x=c(0, 0.5, 0.5, 0), y=c(0.5, 0.5, 1, 1))
abline(0, 1)
```

```{r}
# sufficient conditions w/o nc from above
tt <- truthTable(data_qca[c(1:56, 58:61, 63:70), c(24, 11:12, 14:15, 17)], 
            outcome = c("ACTPART4"), incl.cut1=0.7, sort.by="incl", 
            show.cases = TRUE)
eqmcc(tt, include="?", show.cases = TRUE, details = TRUE)
QCAfit(fsor(data_qca$NB.visibility.hl, fsand(data_qca$NB.gov.depth, 
            data_qca$NB.og.norm)), data_qca$ACTPART4)
# neg. outcome, to check for contradictions
tt <- truthTable(data_qca[c(1:56, 58:61, 63:70), c(24, 11:12, 14:15, 17)], 
            outcome = c("ACTPART4"), incl.cut1=0.7, sort.by="incl", 
            show.cases = TRUE, neg.out = T)
eqmcc(tt, include="?", show.cases = TRUE, details = TRUE)
```

## Transparency Action

```{r}
data_qca$ACTTRANS <- data_qca$ACT.Trans # for QCA package conventions
tt <- truthTable(data_qca[c(1:4, 8:70), c(25, 10:17)], 
            outcome = c("ACTTRANS"), incl.cut1=0.7, sort.by="incl", 
            show.cases = TRUE)
# necessary conditions
superSubset(data_qca[c(1:4, 8:70), c(25, 10:17)], outcome = "ACTTRANS", 
            relation="nec", incl.cut=1, cov.cut=0.4) 
# neg. outcome, to check for contradictions
superSubset(data_qca[c(1:4, 8:70), c(25, 10:17)], outcome = "ACTTRANS", 
            relation="nec", incl.cut=1, cov.cut=0.4, neg.out = T) 
```

```{r, echo=FALSE}
textplot(x = data_qca$NB.dem.mem, y = data_qca$ACTTRANS, words = data_qca$cases, xlim = c(0, 1), ylim = c(0, 1), xlab="Presence of Democratic Members", ylab="Transparency Action")
polygon(x=c(0, 0.5, 0.5, 0), y=c(0.5, 0.5, 1, 1))
abline(0, 1)
```

```{r}
#sufficient condition, without democratic members
tt <- truthTable(data_qca[c(1:4, 8:70), c(25, 10:15, 17)], 
            outcome = c("ACTTRANS"), incl.cut1=0.7, sort.by="incl", 
            show.cases = TRUE)
eqmcc(tt, include="?", show.cases = TRUE, details = TRUE)
# neg. outcome, to check for contradictions
tt <- truthTable(data_qca[c(1:4, 8:70), c(25, 10:15, 17)], 
            outcome = c("ACTTRANS"), incl.cut1=0.7, sort.by="incl", 
            show.cases = TRUE, neg.out = T)
eqmcc(tt, include="?", show.cases = TRUE, details = TRUE)
```

